---
title: "ESM204_HW2"
author: "Katheryn Moya & Nickolas McManus"
date: "4/15/2022"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(here)
library(tidyverse)
library(equatiomatic)
library(broom)
```

```{r}
# read in data
water_districts <-read_csv(here("water_districts.csv"))
```
<br>

### Abatement Costs:

The marginal abatement cost is plotted for each irrigation district below. A linear regression model with zero intercept was added to each graph to indicate (something). (Maybe more explanatory text here). 


```{r}
# for each irrigation district, plot the marginal abatement cost data

## Katheryn: should "quantity of reduction" just be "abatement"?

## Kern County
ggplot(data = water_districts, aes(x = Reduction, y = MC_Kern)) +
  geom_point(color = "slateblue1", size = 1.6, alpha = 0.4) +
  geom_smooth(method = 'lm', se = FALSE, color = "slateblue4")+
  labs(title = "Kern County Marginal Abatement Cost",
         x = "\nquantity of reduction (acre feet)",
         y = "marginal cost ($/acre foot)\n") +
  theme_bw() +
  theme(
    axis.title.x = element_text(face = "bold"),
    axis.title.y = element_text(face = "bold"),
    title = element_text(face = "bold"))

## Mojave County
ggplot(data = water_districts, aes(x = Reduction, y = MC_Mojave)) +
  geom_point(color = "slateblue1", size = 1.6, alpha = 0.4) +
  geom_smooth(method = 'lm', se = FALSE, color = "slateblue4") +
  labs(title = "Mojave County Marginal Abatement Costs",
         x = "\nquantity of reduction (acre feet)",
         y = "marginal cost ($/acre foot)\n") +
  theme_bw() +
  theme(
    axis.title.x = element_text(face = "bold"),
    axis.title.y = element_text(face = "bold"),
    title = element_text(face = "bold"))

## Antelope County
ggplot(data = water_districts, aes(x = Reduction, y = MC_Antelope)) +
  geom_point(color = "slateblue1", size = 1.6, alpha = 0.4) +
  geom_smooth(method = 'lm', se = FALSE, color = "slateblue4")+
  labs(title = "Antelope County Marginal Abatement Costs",
         x = "\nquantity of reduction (acre feet)",
         y = "marginal cost ($/acre foot)\n") +
  theme_bw() +
    theme(
    axis.title.x = element_text(face = "bold"),
    axis.title.y = element_text(face = "bold"),
    title = element_text(face = "bold"))

## Ventura County
ggplot(data = water_districts, aes(x = Reduction, y = MC_Ventura)) +
  geom_point(color = "slateblue1", size = 1.6, alpha = 0.4) +
  geom_smooth(method = 'lm', se = FALSE, color = "slateblue4") +
  labs(title = "Ventura County Marginal Abatement Costs",
         x = "\nquantity of reduction (acre feet)",
         y = "marginal cost ($/acre foot)\n") +
  theme_bw() +
    theme(
    axis.title.x = element_text(face = "bold"),
    axis.title.y = element_text(face = "bold"),
    title = element_text(face = "bold"))
```

```{r, include = FALSE}
# Linear regression model
kern_lm <- lm(MC_Kern ~ 0 + Reduction, data = water_districts)
summary(kern_lm)
kern_tidy <- tidy(kern_lm)
kern_tidy

mojave_lm <- lm(MC_Mojave ~ 0 + Reduction, data = water_districts)
summary(mojave_lm)
mojave_tidy <- tidy(mojave_lm)
mojave_tidy

antelope_lm <- lm(MC_Antelope ~ 0 + Reduction, data = water_districts)
summary(antelope_lm)
antelope_tidy <- tidy(antelope_lm)
antelope_tidy

ventura_lm <- lm(MC_Ventura ~ 0 + Reduction, data = water_districts)
summary(ventura_lm)
ventura_tidy <- tidy(ventura_lm)
ventura_tidy

```

```{r}
# get slopes

A <- kern_lm$coefficient[1]
B <- mojave_lm$coefficient[1]
C <- antelope_lm$coefficient[1]
D <- ventura_lm$coefficient[1]

# create supply/MAC lines
MC_Kern <- function(x) {A*x}
MC_Mojave <- function(x) {B*x}
MC_Antelope <- function(x) {C*x}
MC_Ventura <- function(x) {D*x}

# create demand/MB lines
MB_Kern <- function(x) {343.5 - A*x}
MB_Mojave <-  function(x) {532 - B*x}
MB_Antelope <- function(x) {629.2 - C*x}
MB_Ventura <- function(x) {436.1 - D*x}
```

Take zero-intercept and slope of curves to create marginal abatement curves

- Slope: Kern = `r round(A, 2)`, Mojave = `r round(B, 2)`, Antelope = `r round(C, 2)`, Ventura = `r round(D, 2)` (all positive - demand curve is negative)
- We are provided with E0 (baseline): Kern = 150 AF, Mojave = 140 AF, Antelope = 220 AF, Ventura = 245 AF

### Demand Curves for Water:

- Derive demand curve from MA curve and plot all 4 onto the same graph -> learned how to do that in class #7

```{r}
# Plot all 4 demand curves onto the same graph

ggplot() + 
  xlim(0,245) + 
  ylim(0,650) +
  labs(title = "Predicted Marginal Benefit Curve", 
       x = "\nAcre Foot",
       y = "$/Acre Foot\n",
       color = "Irrigation Districts") +
  geom_function(fun = MB_Kern , aes(color = "Kern"), size = 1) +
  geom_function(fun = MB_Mojave, aes(color = "Mojave"), size = 1) +
  geom_function(fun = MB_Antelope, aes(color = "Antelope"), size = 1) +
  geom_function(fun = MB_Ventura, aes(color = "Ventura"), size = 1) +
  
  theme_bw()
# Antelope is willing to pay the most for the first AF of water
#evaluate scenarios
#could be good to make D agg.
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


### Alternative Policies:

#### Cap without trade
- Reduce each district's water by the same fraction so the 500 AF target is met. Trade is not allowed. 

$755-500=255$
$(255/755)*100 = 33.8%$
$150*0.338=50.7$

```{r}
# cap w/o trade

# Kern
ggplot() + 
  xlim(0,200) + 
  ylim(0,400) +
  geom_function(fun = MC_Kern , aes(color = "Kern"), size = 1) +
  
   # adding vertical line
  geom_segment(aes(x = 50.7, y = 116.1, xend = 50.7, yend = -Inf), linetype = "dashed") +
  
    theme_bw()

```

#### Tax on water use
- A single tax is implemented on all water use in each of the four districts, such that water use is reduced to the 500 AF target.

```{r}
# tax
#naughts are slope
#agg_demand = function(p) {(a0/a1) + (b0/b1) + (c0/c1) + (d0/d1) - ((1/a1)*p) - ((1/b1)*p) - ((1/c1)*p) - ((1/d1)*p)}


a0 <- 343.5
a1 <- 2.29
b0 <- 532
b1 <- 3.8
c0 <- 629.2
c1 <- 2.86
d0 <- 436.1
d1 <- 1.78

agg_demand = function(p) {(a0/a1) + (b0/b1) + (c0/c1) + (d0/d1) - ((1/a1)*p) - ((1/b1)*p) - ((1/c1)*p) - ((1/d1)*p)}

ggplot() + 
  xlim(0,755) + 
  ylim(0,1000) +
  geom_function(fun = agg_demand) +
  geom_function(fun = MB_Kern , aes(color = "Kern"), size = 1) +
  geom_function(fun = MB_Mojave, aes(color = "Mojave"), size = 1) +
  geom_function(fun = MB_Antelope, aes(color = "Antelope"), size = 1) +
  geom_function(fun = MB_Ventura, aes(color = "Ventura"), size = 1)

```


```{r}
#Graph MAC agg instead
agg_MAC = function(x) {(1/((1/A)+(1/B)+(1/C)+(1/D)))*x}

ggplot() + 
  xlim(0,500) + 
  ylim(0,500) +
  geom_function(fun = agg_MAC, size = 1) +
  geom_function(fun = MC_Kern , aes(color = "Kern"), size = 1) +
  geom_function(fun = MC_Mojave, aes(color = "Mojave"), size = 1) +
  geom_function(fun = MC_Antelope, aes(color = "Antelope"), size = 1) +
  geom_function(fun = MC_Ventura, aes(color = "Ventura"), size = 1)+
  
    # adding vertical line
  geom_segment(aes(x = 255, y = 158.39, xend = 255, yend = -Inf), linetype = "dashed") +
  
  # adding horizontal line
  geom_segment(aes(x = 255, y = 158.39, xend = -Inf, yend = 158.39), linetype = "dashed") +
 
    theme_bw()
```

```{r}
b <- ggplot(mtcars, aes(wt, mpg)) +
  geom_point()

df <- data.frame(x1 = 2.62, x2 = 3.57, y1 = 21.0, y2 = 15.0)
b +
 geom_curve(aes(x = x1, y = y1, xend = x2, yend = y2, colour = "curve"), data = df) +
 geom_segment(aes(x = x1, y = y1, xend = x2, yend = y2, colour = "segment"), data = df)

b + geom_curve(aes(x = x1, y = y1, xend = x2, yend = y2), data = df, curvature = -0.2)
b + geom_curve(aes(x = x1, y = y1, xend = x2, yend = y2), data = df, curvature = 1)
b + geom_curve(
  aes(x = x1, y = y1, xend = x2, yend = y2),
  data = df,
  arrow = arrow(length = unit(0.03, "npc"))
)
```




#### Cap and trade
- Cap water use, but allow trade across districts. How much water is used by each district after trade? 

```{r}
# cap and trade

```


### The Cost of Drought:

Water use must be reduced from 500AF to 300AF. 

```{r}
# some code here

```


